European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-29 manuscript/manuscript.qmd
Add fiscal table to appendix
Add 1st para to robustness checks

@@

>>>>

## Alternative Measure of Conditionality

Another concern is that our results on conditionality could be sensitive to the way IMF programme conditions are measured. Our baseline analysis follows @lipscy2018, who aggregate the total number of conditions across five-year periods. Yet, as @guimaraes2021 note, the overall count of IMF conditions, although widely used, may not fully capture the *stringency* of conditionality. They therefore propose alternative indicators, including the number of *fiscal* conditions and the required fiscal adjustment (RFA), to reassess the relationship between political alignment and conditionality. To address this concern, we replicate our conditionality model (the fourth specification in @tbl-results) using these alternative measures as dependent variables, and present the results in Appendix [-@sec-fiscal].

@@

# Fiscal Conditions {#sec-fiscal .appendix}

```{r}
#| label: tbl-results-fiscal
#| tbl-cap: Effects of US and European Influence on IMF fiscal conditionality (1999–2012)
#| tbl-pos: H
load('save/regTable_fiscal.RData')
resultsTable |> tinytable::theme_latex(resize_width = 1, resize_direction = "down")
```
